---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# pollofpolls

The goal of pollofpolls is to make it easy to make a poll of polls.

This package is open sourced and all contributions are welcome. I have made
some methodological choices in this implementation that you are more than welcome
to challenge. 

Please do so by raising issues here on github and / or by creating new functions
and doing a pull request. 

In the code of each function I have tried to document my choices as good as possible.
Please raise an issue if you feel something is wrong or missing.

### Several poll of polls methods

There are now two methods available for calculating poll of polls:

#### The FiveThirtyEight Way

The methodology used is based on these two articles:

https://greenbookblog.org/2018/01/16/the-prediction-how-nate-silver-does-it/

https://fivethirtyeight.com/features/the-polls-are-all-right/

This is the way used in example one and two

#### The Altinget Way 

The methodology there is based on hear say. It is pretty intuitive - read the 
documentation for the function: pp_poll_of_poll_summariser()

This is the way used in example three.

## Installation

You can install pollofpolls from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("mikkelkrogsholm/pollofpolls")
```

## Example one: Driverless poll of polls

This is hands free driverless poll of polls calculation. 

```{r driverless}
library(pollofpolls)

pollofpoll <- suppressMessages(pp_auto_poll_of_poll()) 

# Round the digits so it looks pretty
pollofpoll[, 1:2] <- purrr::map(pollofpoll[, 1:2], round, 2)

# Make a better looking table
knitr::kable(pollofpoll)
```

## Example two: Run down of each function

This is basically a run through of each part of the driverless poll of polls.

```{r run_down}
library(pollofpolls)

# Download the raw polls
raw_polls <- pp_get_raw_polls()

# Do a check on the polls
checked_polls <- pp_check_raw_polls(raw_polls = raw_polls, silent = TRUE)

# Calculate the pollster rating
pollster_rating <- pp_calc_pollster_rating()

# Add weights to the polls
polls_with_wt <- pp_add_weights(checked_polls = checked_polls, 
                                pollster_rating = pollster_rating)

# Calculate the final pole
final_poll <- pp_calc_poll(polls_with_wt = polls_with_wt)

# Round the digits so it looks pretty
final_poll[, 1:2] <- purrr::map(final_poll[, 1:2], round, 2)

# Make a better looking table
knitr::kable(final_poll)
```

## Example three:  Poll of Polls by summarisation

This is the way I hear they do it at altinget.

```{r altinget}
library(pollofpolls)

polls <- pp_get_raw_polls()

my_pp <- pp_poll_of_poll_summariser(polls)

# Round the digits so it looks pretty
my_pp[, 1:2] <- purrr::map(my_pp[, 1:2], round, 2)

# Make a better looking table
knitr::kable(my_pp)
```


### Comparing methods

The two methods are very alike when it comes to predicting the results

```{r compare_1}
library(tidyverse)

plotdata <- inner_join(pollofpoll, my_pp, by = "party")

ggplot(plotdata) + 
  geom_point(aes(pred.x, pred.y)) + 
  theme_minimal() + 
  labs(y = "Altinget",
       x = "FiveThirtyEight") + 
  expand_limits(x = c(0, max(plotdata$pred.y)), 
                y = c(0, max(plotdata$pred.x))) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray") +
  coord_equal()
```

... but very different when it comes to estimating the error. One uses a formula based error and the other a more empirically derived one. And it shows.

```{r compare_2}
ggplot(plotdata) + 
  geom_point(aes(error.x, error.y)) + 
  theme_minimal() + 
  labs(y = "Altinget",
       x = "FiveThirtyEight") + 
  expand_limits(x = c(0, max(plotdata$error.y)), 
                y = c(0, max(plotdata$error.x))) +
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "gray") +
  coord_equal()
```
